\Large \bf SIRIUS: A Revolutionary Approach to I/O and Storage for Exascale Scientific Computing

### 2016-03-11 papers/2016-HotStorage/paper.tex
fixed typo
fixed L2 norm.

\subsection*{Abstract}
The longest existing parallel I/O APIs, HDF5, PnetCDF, and NetCDF, are focused
on treating the entire output from a parallel application as a single unit.
These libraries work to gather the data from all processes and arrange it such
that it is organized much like as if it were written from a single process.
This approach, in particular the two-phase collective I/O with data sieving
portion, has proven difficult to scale for 3-D domain decompositions at scale.
ADIOS shifted the focus from treating the entire application output as a single
entity to treating the output from each writer as a self-contained entity. This
eliminated the need for the problematic two-phase collective I/O and has
demonstrated good scalability well into the petascale era. Another shift is
required to address the needs of exascale systems. New supercomputing system
I/O bandwidth is not keeping pace with the compute acceleration leading to
accute bottlenecks.  While ``burst buffer'' technology will help address the
performance gap, it does not address the problem completely. This paper
describes a new approach to not just an I/O library, but also the underlying
storage infrastructure to address the needs of exascacle applications cognizant
of projected exascale platform characteristics and in the context of current
industry trends.

@@

Evaluating the error when using just the 3-byte portion compared to the full
data set yields an $L^2$ norm of 72028.2 and $L_{\inf}$ of 0.00109242.

>>>>

\subsection*{Abstract}
The longest existing parallel I/O APIs, HDF5, PnetCDF, and NetCDF, are focused
on treating the entire output from a parallel application as a single unit.
These libraries work to gather the data from all processes and arrange it such
that it is organized much like as if it were written from a single process.
This approach, in particular the two-phase collective I/O with data sieving
portion, has proven difficult to scale for 3-D domain decompositions at scale.
ADIOS shifted the focus from treating the entire application output as a single
entity to treating the output from each writer as a self-contained entity. This
eliminated the need for the problematic two-phase collective I/O and has
demonstrated good scalability well into the petascale era. Another shift is
required to address the needs of exascale systems. New supercomputing system
I/O bandwidth is not keeping pace with the compute acceleration leading to
acute bottlenecks.  While ``burst buffer'' technology will help address the
performance gap, it does not address the problem completely. This paper
describes a new approach to not just an I/O library, but also the underlying
storage infrastructure to address the needs of exascacle applications cognizant
of projected exascale platform characteristics and in the context of current
industry trends.

@@

Evaluating the error when using just the 3-byte portion compared to the full
data set yields an $L^2$ norm of 0.000087925 and $L_{\inf}$ of 0.00109242.
